Policing for Profit and the Mobilization of Black Voters

### 2021-03-28 markdown/draft_paper.Rmd
write

Before testing the causal effect of fees and fines collections, we begin with a cross-sectional analysis of the relationship between fees and fines and turnout. Here, we regress municipality-level turnout in 2018 against fees and fines collections as reported in the 2017 COG, as well as a number of other covariates. In Figure \ref{fig:mef-2018} we present the marginal effect of fees and fines on municipal-level turnout. The plot shows the results from two separate models: one in which the dependent variable is Black turnout (as a share of CVAP), and a second in which the dependent variable is non-Black turnout. The figure also marks the interdecile range. The full regression table can be found in Appendix XX.

```{r cross-18, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 5, fig.cap = "\\label{fig:mef-2018}Marginal Effect of per-capita Fees and Fines on Turnout, 2018", fig.pos = "H", fig.align = "center"}
load("temp/mef_to.rdata")
print(p2)
```

@@

\begin{singlespace}
```{r balance-tab-chunk, echo = F}
t <- readRDS("./temp/balance_table_y.rds")
j <- knitr::kable(t, booktabs = T, caption = "(\\#tab:balance) Balance Table", linesep = "",
                  escape = F) %>%
  add_header_above(c(" " = 1, "Means: Unmatched Data" = 2, "Means: Matched Data" = 2, "Percent Improvement" = 4), align = "c") %>%
  kable_styling(latex_options = c("scale_down", "HOLD_position"))
j
```
\end{singlespace}

>>>>

Before testing the causal effect of fees and fines collections, we begin with a cross-sectional analysis of the relationship between fees and fines and turnout using ordinary least squares. Here, we regress municipality-level turnout in 2018 against fees and fines collections as reported in the 2017 COG, as well as a number of other covariates. In Figure \ref{fig:mef-2018} we present the marginal effect of fees and fines on municipal-level turnout. The plot shows the results from two separate models: one in which the dependent variable is Black turnout (as a share of CVAP), and a second in which the dependent variable is non-Black turnout. The figure also marks the interdecile range. The full regression table can be found in Appendix XX.

```{r cross-18, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 5, fig.cap = "\\label{fig:mef-2018}Predicted Turnout, 2018", fig.pos = "H", fig.align = "center"}
load("temp/mef_to.rdata")
print(p2)
```

@@

\begin{singlespace}
```{r balance-tab-chunk, echo = F}
t <- readRDS("temp/balance_table_y.rds")
j <- knitr::kable(t, booktabs = T, caption = "(\\#tab:balance) Balance Table", linesep = "",
                  escape = F) %>%
  add_header_above(c(" " = 1, "Means: Unmatched Data" = 2, "Means: Matched Data" = 2, "Percent Improvement" = 4), align = "c") %>%
  kable_styling(latex_options = c("scale_down", "HOLD_position"))
j
```
\end{singlespace}

### 2021-03-28 markdown/draft_paper.tex
write

\title{Policing for Profit and the Mobilization of Black Voters}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{Fines, Fees, and Turnout}
\author{Jonathan Ben-Menachem\footnote{PhD Student, Columbia University, Department of Sociology (\href{mailto:jb4487@columbia.edu}{\nolinkurl{jb4487@columbia.edu}})} \and Kevin Morris\footnote{PhD Student, CUNY Graduate Center, Department of Sociology (\href{mailto:kmorris@gradcenter.cuny.edu}{\nolinkurl{kmorris@gradcenter.cuny.edu}})}}
\date{March 19, 2021}

@@

Before testing the causal effect of fees and fines collections, we begin with a cross-sectional analysis of the relationship between fees and fines and turnout. Here, we regress municipality-level turnout in 2018 against fees and fines collections as reported in the 2017 COG, as well as a number of other covariates. In Figure \ref{fig:mef-2018} we present the marginal effect of fees and fines on municipal-level turnout. The plot shows the results from two separate models: one in which the dependent variable is Black turnout (as a share of CVAP), and a second in which the dependent variable is non-Black turnout. The figure also marks the interdecile range. The full regression table can be found in Appendix XX.

@@

\caption{\label{fig:mef-2018}Marginal Effect of per-capita Fees and Fines on Turnout, 2018}\label{fig:cross-18}
\end{figure}

@@

\caption{\label{tab:balance-tab-chunk}\label{tab:balance} Balance Table}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lllllllll}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Means: Unmatched Data} & \multicolumn{2}{c}{Means: Matched Data} & \multicolumn{4}{c}{Percent Improvement} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-9}
 & Treated & Control & Treated & Control & Mean Diff & eQQ Med & eQQ Mean & eQQ Max\\
\midrule
\%White & 49.2\% & 49.5\% & 49.2\% & 49.2\% & 82.05 & 82.05 & 82.05 & 82.05\\
\% Black & 23.1\% & 21.0\% & 23.1\% & 23.2\% & 92.48 & 92.48 & 92.48 & 92.48\\
\% Latino & 18.8\% & 20.0\% & 18.8\% & 19.0\% & 79.27 & 79.27 & 79.27 & 79.27\\
\% Asian & 2.2\% & 2.4\% & 2.2\% & 2.2\% & 98.45 & 98.45 & 98.45 & 98.45\\
\% Male & 50.8\% & 49.8\% & 50.8\% & 50.8\% & 99.80 & 99.80 & 99.80 & 99.80\\
\% Democrat & 42.0\% & 40.2\% & 42.0\% & 42.1\% & 92.87 & 92.87 & 92.87 & 92.87\\
\% Republican & 24.6\% & 24.7\% & 24.6\% & 24.6\% & 100.00 & 100.00 & 100.00 & 100.00\\
Age & 43.4 & 42.4 & 43.4 & 42.8 & 41.67 & -263.67 & 38.10 & 73.02\\
Registration Date & 2006-06-27 & 2007-09-21 & 2006-06-27 & 2006-11-09 & 69.91 & 37.60 & 73.79 & 74.70\\
Pre-2012 Tickets & 1.3 & 0.8 & 1.3 & 1.3 & 95.12 & 93.14 & 95.12 & 96.30\\
Turnout\textsubscript{t=-3} & 33.2\% & 27.7\% & 33.2\% & 33.2\% & 99.99 & 99.99 & 99.99 & 99.99\\
Turnout\textsubscript{t=-2} & 29.0\% & 25.9\% & 29.0\% & 29.0\% & 100.00 & 100.00 & 100.00 & 100.00\\
Turnout\textsubscript{t=-1} & 47.1\% & 37.7\% & 47.1\% & 47.1\% & 99.89 & 99.89 & 99.89 & 99.89\\
Median Income & \$63,885 & \$64,604 & \$63,885 & \$63,470 & 42.40 & 7.10 & -10.35 & -32.49\\
\% with Some College & 74.6\% & 75.0\% & 74.6\% & 74.7\% & 67.33 & 27.90 & 29.43 & 15.52\\
Unemployment Rate & 6.5\% & 6.3\% & 6.5\% & 6.3\% & -40.04 & -226.05 & -158.07 & -108.94\\
\bottomrule
\end{tabular}}
\end{table}
\end{singlespace}

>>>>

\title{Policing for Profit and the Mobilization of Black Voters}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{Fines, Fees, and Turnout}
\author{Jonathan Ben-Menachem\footnote{PhD Student, Columbia University, Department of Sociology (\href{mailto:jb4487@columbia.edu}{\nolinkurl{jb4487@columbia.edu}})} \and Kevin Morris\footnote{PhD Student, CUNY Graduate Center, Department of Sociology (\href{mailto:kmorris@gradcenter.cuny.edu}{\nolinkurl{kmorris@gradcenter.cuny.edu}})}}
\date{March 25, 2021}

@@

Before testing the causal effect of fees and fines collections, we begin with a cross-sectional analysis of the relationship between fees and fines and turnout using ordinary least squares. Here, we regress municipality-level turnout in 2018 against fees and fines collections as reported in the 2017 COG, as well as a number of other covariates. In Figure \ref{fig:mef-2018} we present the marginal effect of fees and fines on municipal-level turnout. The plot shows the results from two separate models: one in which the dependent variable is Black turnout (as a share of CVAP), and a second in which the dependent variable is non-Black turnout. The figure also marks the interdecile range. The full regression table can be found in Appendix XX.

@@

\caption{\label{fig:mef-2018}Predicted Turnout, 2018}\label{fig:cross-18}
\end{figure}

@@

\caption{\label{tab:balance-tab-chunk}\label{tab:balance} Balance Table}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lllllllll}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Means: Unmatched Data} & \multicolumn{2}{c}{Means: Matched Data} & \multicolumn{4}{c}{Percent Improvement} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-9}
 & Treated & Control & Treated & Control & Mean Diff & eQQ Med & eQQ Mean & eQQ Max\\
\midrule
\%White & 45.8\% & 47.4\% & 45.8\% & 45.8\% & 99.70 & 99.70 & 99.70 & 99.70\\
\% Black & 26.1\% & 23.0\% & 26.1\% & 26.1\% & 99.85 & 99.85 & 99.85 & 99.85\\
\% Latino & 19.1\% & 20.2\% & 19.1\% & 19.1\% & 99.97 & 99.97 & 99.97 & 99.97\\
\% Asian & 2.0\% & 2.3\% & 2.0\% & 2.0\% & 100.00 & 100.00 & 100.00 & 100.00\\
\% Male & 51.9\% & 50.8\% & 51.9\% & 51.2\% & 36.61 & 36.46 & 36.46 & 36.46\\
\% Democrat & 43.6\% & 41.6\% & 43.6\% & 43.3\% & 86.44 & 86.44 & 86.44 & 86.44\\
\% Republican & 22.9\% & 23.7\% & 22.9\% & 22.0\% & -5.57 & -5.57 & -5.57 & -5.57\\
Age & 42.7 & 42.4 & 42.7 & 42.2 & -67.69 & 11.98 & 33.08 & 70.35\\
Registration Date & 2006-09-25 & 2007-08-20 & 2006-09-25 & 2006-10-21 & 92.30 & 60.54 & 91.16 & 93.26\\
Stops in pre-period & 2.248 & 1.437 & 2.248 & 2.206 & 94.79 & 69.37 & 94.81 & 95.91\\
Turnout\textsubscript{t=-3} & 32.4\% & 28.4\% & 32.4\% & 32.5\% & 97.59 & 97.59 & 97.59 & 97.59\\
Turnout\textsubscript{t=-2} & 30.2\% & 27.5\% & 30.2\% & 30.2\% & 99.94 & 99.94 & 99.94 & 99.94\\
Turnout\textsubscript{t=-1} & 45.0\% & 38.2\% & 45.0\% & 45.0\% & 99.97 & 99.97 & 99.97 & 99.97\\
Median Income & \$62,193 & \$63,412 & \$62,193 & \$62,111 & 93.27 & 82.89 & 79.16 & 68.07\\
\% with Some College & 73.8\% & 74.4\% & 73.8\% & 73.9\% & 78.57 & 53.38 & 57.55 & 53.15\\
Unemployment Rate & 6.7\% & 6.5\% & 6.7\% & 6.6\% & 49.02 & -19.29 & -20.95 & -17.34\\
\bottomrule
\end{tabular}}
\end{table}
\end{singlespace}
